Spin canonical rings of log stacky curves

### 2015-07-08 curves-write-up/arXiv versions/spin_cring_arXiv_v1.tex
remove subfiles, minor edits

\usepackage{amsmath}
\usepackage{amsxtra}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{eucal}
\usepackage[all]{xy}
\usepackage{graphicx}
\usepackage{tikz-cd}
\usepackage{mathrsfs}
\usepackage{subfiles}
\usepackage{euler}
\usepackage{hyperref}
\usepackage{color}
\usepackage{longtable}
\usepackage{float}
\usepackage{caption}

@@

Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.  In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two cases we explicitly construct specific base cases and present a finite list of exceptional cases, whereas in the genus $g \geq 2$ case we deduce base cases from more general arguments.
\begin{rem}
\label{rem:explicit-generators}
%The main theorem obtains bounds on the degrees of the generators
%and relations of log spin canonical rings. 
In addition to providing bounds on the degrees of generators and relations of log spin canonical rings, the proof
of the genus one and genus zero cases of our main theorem also yield explicit systems
of generators and initial ideals of relations, as described in Remarks ~\ref{rem:genus-1-explicit-bound} and ~\ref{rem:genus-0-explicit-bound}.
Furthermore, our proof of the genus $g \geq 2$ case provides
an inductive procedure for explicitly determining the generators
and initial ideal of relations of a log spin canonical ring given a presentation of the corresponding ring on the coarse space, but actually computing such a presentation of log spin canonical on the coarse space can be difficult.  Many
explicit systems of generators and relations for curves of genus $2
\leq g \leq 15$ are detailed in interesting examples by Neves
\cite[Section III.4]{neves:halfcan}. 
\end{rem}
\begin{rem}
The explicit construction described in Remark ~\ref{rem:explicit-generators} also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
Specifically, in almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$. For further detail, see Remarks ~\ref{rem:genus-0-explicit-bound}, ~\ref{rem:genus-1-explicit-bound}, and ~\ref{rem:genus-2-explicit-bound} in the cases that the genus is $0,1,$ or $\geq 2$ respectively.
\end{rem}

@@

\begin{rem}
\label{rem:genus-2-explicit-bound}
For this remark, we retain the terminology from the proof of Theorem ~\ref{thm:g-high-main}.
Suppose $e :=  \max(e_1,\ldots, e_r).$ Then, $R_L$ has a generator in degree $e$ when $e \geq 5$ and a relation in degree at least $2e-4$ when $e \geq 7$. Since the proof of Theorem ~\ref{thm:g-1-main} is given by inductively 
applying Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2}, we obtain that $R_L$ is minimally generated over $R_{L'}$ by an element in degree $e,$ assuming $e \geq 5$. Furthermore, if $e \geq 7$ and $e_i = e,$ 
then there must be a relation with leading term $y_{i,e_i} \cdot y_{i,e_i-4}.$ Hence, there is a relation in degree at least $2e - 4$. 
Further, by examining the statements of Lemma ~\ref{lem:sat-1} and \ref{lem:sat-2} in the case that there are $1 \leq i < j \leq r$ with $e_i = e_j = e$, then, there is necessarily a relation with leading term $y_{i, e_i} \cdot y_{j, e_j}$ in degree $2e$.

This analysis also applies to the cases that $g = 0$ and $g = 1$.
\end{rem}

>>>>

\usepackage{amsmath}
\usepackage{amsxtra}
\usepackage{amscd}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{eucal}
\usepackage[all]{xy}
\usepackage{graphicx}
\usepackage{tikz-cd}
\usepackage{mathrsfs}
\usepackage{euler}
\usepackage{hyperref}
\usepackage{color}
\usepackage{longtable}
\usepackage{float}
\usepackage{caption}

@@

Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.  In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two cases we explicitly construct specific base cases and present a finite list of exceptional cases, whereas in the genus $g \geq 2$ case we deduce base cases from more general arguments.

\begin{rem}
\label{rem:explicit-generators}
%The main theorem obtains bounds on the degrees of the generators
%and relations of log spin canonical rings. 
In addition to providing bounds on the degrees of generators and relations of log spin canonical rings, the proof
of the genus one and genus zero cases of our main theorem also yield explicit systems
of generators and initial ideals of relations, as described in Remarks ~\ref{rem:genus-1-explicit-bound} and ~\ref{rem:genus-0-explicit-bound}.
Furthermore, our proof of the genus $g \geq 2$ case provides
an inductive procedure for explicitly determining the generators
and initial ideal of relations of a log spin canonical ring given a presentation of the corresponding ring on the coarse space, but actually computing such a presentation of log spin canonical on the coarse space can be difficult.  Many
explicit systems of generators and relations for curves of genus $2
\leq g \leq 15$ are detailed in interesting examples by Neves
\cite[Section III.4]{neves:halfcan}. 
\end{rem}

\begin{rem}
The explicit construction described in Remark ~\ref{rem:explicit-generators} also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
In almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$. For further detail, see Remarks ~\ref{rem:genus-0-explicit-bound}, ~\ref{rem:genus-1-explicit-bound}, and ~\ref{rem:genus-2-explicit-bound} in the cases that the genus is $0,1,$ or $\geq 2$ respectively.
\end{rem}

@@

\begin{rem}
\label{rem:genus-2-explicit-bound}
For this remark, we retain the terminology from the proof of Theorem ~\ref{thm:g-high-main}.
Suppose $e :=  \max(e_1,\ldots, e_r).$ Then, $R_L$ has a generator in degree $e$ when $e \geq 5$ and a relation in degree at least $2e-4$ when $e \geq 7$. Since the proof of Theorem ~\ref{thm:g-1-main} is given by inductively 
applying Lemmas ~\ref{lem:sat-1} and ~\ref{lem:sat-2}, we obtain that $R_L$ is minimally generated over $R_{L'}$ by an element in degree $e,$ assuming $e \geq 5$. Furthermore, if $e \geq 7$ and $e_i = e,$ 
then there must be a relation with leading term $y_{i,e_i} \cdot y_{i,e_i-4}.$ Hence, there is a relation in degree at least $2e - 4$. 
Further, by examining the statements of Lemma ~\ref{lem:sat-1} and \ref{lem:sat-2} in the case that there are $1 \leq i < j \leq r$ with $e_i = e_j = e$, then, there is necessarily a relation with leading term $y_{i, e_i} \cdot y_{j, e_j}$ in degree $2e$. This analysis also applies to the cases that $g = 0$ and $g = 1$.
\end{rem}

### 2015-07-08 curves-write-up/spin_cring.tex
remove subfiles, minor edits

%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%
%%%%%%%%%%%%%%%

@@

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian group}, i.e.,~ a discrete subgroup of
$\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations, such that $\Gamma \backslash \BH$ has finite area.
We consider the graded {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best ways to describe the ring $M(\Gamma)$ is to write down a presentation.
%of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
To do so, it is useful to have a bound on the
degrees in which the generators and relations can occur. In the
special case that $\Gamma$ has no odd weight modular forms, Voight
and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
We extend their result to all Fuchsian groups $\Gamma$ in the main
theorem of this work.

We can now consider the orbifold $\Gamma \backslash \BH$ over $\BC$.
For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
\backslash \BH$ is a Riemann surface over $\BC$. 
$\Gamma \backslash \BH$ may be non-compact, but in such cases we can form a
compact Riemann surface, $\Gamma \backslash \BH^*,$ by adding in
cusps, with associated divisor of cusps $\Delta$.

@@

%$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e.,~ $c_i, c_j \le

@@

%\] is a divisor of $X$ (i.e.,~ with 

@@

\begin{rem}
Since all points are linearly equivalent on $\BP^1_\Bk$, we may
assume without loss of generality that $\halfcan_X = n \infty$ for some $n
\in \BN$ and $K_X = -2 \infty$. We will use this convention
throughout this section.
\end{rem}

@@

\begin{lem}
\label{lem:g-0-admissible-cases}
Let $(\sx', \Delta, \halfcan')$ be a log spin curve with signature
$\sigma := (0; e_1, \ldots, e_r; 0)$. Then, $R' := R_{\halfcan'}$ is
generated by elements of degree at most $e = \max(5 , e_1, \ldots,
e_r)$ with relations in degree at most $2e$. Furthermore, each of
the cases in Table ~\ref{table:g-0-base-cases} satisfy the
conditions of Lemma ~\ref{lem:raise-stacky-order} (i.e.,~ either $(\sx',
\halfcan', J) = (\sx', -\infty + \sum_{i = 1}^{r} \subhalf{e_i}
P_i, J)$ is admissible or the stabilizer orders are all $3$ as per
Case ~\ref{custom:three-cases-1} of Remark ~\ref{rem:three-cases}):

>>>>

%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian group}, i.e.~ a discrete subgroup of
$\PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations, such that $\Gamma \backslash \BH$ has finite area.
We consider the graded {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$. One of the best ways to describe the ring $M(\Gamma)$ is to write down a presentation.
%of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
To do so, it is useful to have a bound on the
degrees in which the generators and relations can occur. In the
special case that $\Gamma$ has no odd weight modular forms, Voight
and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
We extend their result to all Fuchsian groups $\Gamma$ in the main
theorem of this work.

We can now consider the orbifold $\Gamma \backslash \BH$ over $\BC$.
For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
\backslash \BH$ is a Riemann surface over $\BC$. 
Although $\Gamma \backslash \BH$ may be non-compact, we can form a
compact Riemann surface $\Gamma \backslash \BH^*$ by adding in
cusps (with associated divisor of cusps $\Delta$).

@@

%$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e.~ $c_i, c_j \le

@@

%\] is a divisor of $X$ (i.e.~ with 

@@

\begin{rem}
Since all points are linearly equivalent on $\BP^1_\Bk$, 
$\halfcan_X \sim n \infty$ for some $n \in \BN$ and
$K_X \sim -2 \infty$. We will use this convention
throughout this section.
\end{rem}

@@

\begin{lem}
\label{lem:g-0-admissible-cases}
Let $(\sx', \Delta, \halfcan')$ be a log spin curve with signature
$\sigma := (0; e_1, \ldots, e_r; 0)$. Then, $R' := R_{\halfcan'}$ is
generated by elements of degree at most $e = \max(5 , e_1, \ldots,
e_r)$ with relations in degree at most $2e$. Furthermore, each of
the cases in Table ~\ref{table:g-0-base-cases} satisfy the
conditions of Lemma ~\ref{lem:raise-stacky-order} (i.e.~ either $(\sx',
\halfcan', J) = (\sx', -\infty + \sum_{i = 1}^{r} \subhalf{e_i}
P_i, J)$ is admissible or the stabilizer orders are all $3$ as per
Case ~\ref{custom:three-cases-1} of Remark ~\ref{rem:three-cases}):
